\begin{center}
    \huge \textbf{Acknowledgment}
\end{center}
\vspace{15mm}
I would like to express my acknowledgment and appreciation for the Unboxing an Industry-Level Deep Learning Model for Brain Anomaly Detection: An Elaborative Study. We are humbled by the depth of expertise, support, and encouragement that has enabled us to complete this project as we set out on this challenging road to unbox an industry-level deep learning model for brain anomaly detection. Without the coordinated efforts, advice, and inspiration of several people and institutions, to whom we sincerely apologies, the realization of this study would not have been possible. We would like to convey our sincere gratitude to the patients and their families who voluntarily took part in medical research and provided us with essential information and insights for this study. Your bravery and determination to advance science highlight the importance of our work and serve as a reminder of the practical relevance at the core of our work. We would like to express our sincere gratitude to the radiologists, medical professionals, and other specialists who kindly contributed their knowledge and skills to this project. Our understanding of the difficulties and complexity involved in brain abnormality detection has been significantly shaped by your advice, and your commitment to patient care motivates us to strive for perfection in our work. We owe a debt of gratitude to our mentors and advisors for their persistent encouragement, guidance, and helpful criticism. Your knowledge and expertise have been our compass, pointing us in the direction of our study and inspiring us to think critically and creatively. Additionally, we want to thank all of our coworkers and collaborators whose friendship and cooperation have enriched our scientific experience. Your unique viewpoints and thoughts have helped to create a space for intellectual development and discovery. We recognize that this effort is a monument to the strength of cooperation, tenacity, and the quest of knowledge as we share this detailed study on developing an industry-level deep learning model for brain abnormality detection. We dedicate this work to everyone who has helped enhance medical diagnostics and the pursuit of better healthcare outcomes through the transformational potential of artificial intelligence, whether directly or indirectly.