\begin{center}
    \huge \textbf{Dedication}
\end{center}
\vspace{15mm}
This initiative honours the innumerable people whose lives have been affected by neurological conditions and brain irregularities and pays homage to the never-ending quest for knowledge and the unflagging spirit of creativity. We humbly give our dedication to developing medical diagnostics through cutting-edge technology to the patients, their families, and the hardworking healthcare professionals who work to alleviate pain and restore hope. We dedicate our work with the utmost respect to individuals who bravely and tenaciously overcome the difficulties presented by brain irregularities, serving as our inspiration as we push the boundaries of artificial intelligence and medical imaging. A future in which early and precise detection of brain irregularities is our motivation for understanding and utilizing the power of deep learning. May this project serve as a monument to the potential of multidisciplinary research and its transformative power. We applaud the joint efforts of researchers, medical professionals, and engineers whose collaboration drives progress and improves human life in our pursuit of creating an industry-level deep learning model for brain abnormality identification. We have a common desire to have a long-lasting impact on patients' lives and the worldwide healthcare community as we set out on our adventure to unpack the complexities of deep learning for brain abnormality identification. We embark on this project with steadfast commitment and the guiding values of integrity, accountability, and compassion in the hopes that our efforts will chime with the spirit of advancement.