\begin{center}
    \section*{Abstract}
\end{center}
The image-to-text conversion is a popular topic in the field of Artificial Intelligence (AI) and Computer Vision. The aim of this project is to develop a system that can recognize and convert the text present in an image into machine-readable format. The system is based on deep learning techniques that use Convolutional Neural Networks (CNNs) and Recurrent Neural Networks (RNNs) to process the input image and generate a corresponding text output. The proposed system consists of two main stages: image pre-processing and text generation. In the image pre-processing stage, the input image is first pre-processed to remove noise and enhance its quality. Then, the pre-processed image is fed into the CNNs to extract features from the image. In the text generation stage, the output of the CNNs is passed through the RNNs to generate the corresponding text output. The system is trained on a large dataset of images containing text. The dataset is pre-processed and annotated to provide accurate text information for each image. The system is evaluated on a separate test dataset to measure its accuracy and performance. The results of the evaluation show that the proposed system is capable of accurately recognizing and converting the text present in an image into machine-readable format. The system achieves high accuracy rates and performs well on both synthetic and real-world images containing text. In conclusion, the proposed image-to-text conversion system based on deep learning techniques has the potential to be a useful tool for various applications such as document scanning and recognition, text translation, and information retrieval.

% for a MNIST data set.