\section{Conclusion}
\subsection{Conclusion:}
In conclusion, the ItOD-AD system is a significant advancement in the field of assistive technology for the visually impaired. It utilizes machine learning techniques to convert images into object detections and generates audio descriptions for the detected objects. The system provides a practical and efficient solution for the visually impaired to access visual information and enhance their understanding of the surrounding environment. ItOD-AD has the potential to significantly improve the quality of life for visually impaired individuals, and its effectiveness has been demonstrated through extensive testing and evaluations. The system's accuracy and efficiency make it a promising solution for future research and development in the field of assistive technology. Overall, ItOD-AD is an excellent example of how technology can be leveraged to improve the lives of individuals with disabilities, and its contributions to the field of assistive technology are invaluable.
\subsection{Future Work Extension:}
The current state of the problem is that blind individuals are often unable to recognize objects in their environment and have limited access to visual information. Existing solutions such as Braille labels and audio descriptions have limitations in terms of scalability and efficiency.\\
The motivation behind ItOD-AD is to improve the quality of life for visually impaired individuals by providing them with a more efficient and scalable means of accessing visual information. The proposed solution can help blind individuals navigate their environment, recognize objects, and better understand the world around them.

