
\begin{thebibliography}{99}
\bibitem{b1}Rajendran, P. Selvi, Padmaveni Krishnan, and D. John Aravindhar. "Design and Implementation of Voice Assisted Smart Glasses for Visually Impaired People Using Google Vision API." 2020 4th International Conference on Electronics, Communication and Aerospace Technology (ICECA). IEEE, 2020.
\bibitem{b2}Suresh, Aswath, et al. "Intelligent smart glass for visually impaired using deep learning machine vision techniques and robot operating system (ROS)." Robot Intelligence Technology and Applications 5: Results from the 5th International Conference on Robot Intelligence Technology and Applications 5. Springer International Publishing, 2019.
\bibitem{b3}Chava, Teja, et al. "IoT based Smart Shoe for the Blind." 2021 6th International Conference on Inventive Computation Technologies (ICICT). IEEE, 2021.
\bibitem{b4}Agarwal, Rohit, et al. "Low cost ultrasonic smart glasses for blind." 2017 8th IEEE Annual Information Technology, Electronics and Mobile Communication Conference (IEMCON). IEEE, 2017.

\bibitem{b5}Younis, Ola, et al. "A hazard detection and tracking system for people with peripheral vision loss using smart glasses and augmented reality." International Journal of Advanced Computer Science and Applications 10.2 (2019): 1-9.

\bibitem{b6}AlSaid, Hawra, et al. "Deep learning assisted smart glasses as educational aid for visually challenged students." 2019 2nd International Conference on new Trends in Computing Sciences (ICTCS). IEEE, 2019.
\bibitem{b7}Leh, Nor Adni Mat, et al. "Smart irrigation system using internet of things." 2019 IEEE 9th International Conference on System Engineering and Technology (ICSET). IEEE, 2019.
\bibitem{b8}Chava, Teja, et al. "IoT based Smart Shoe for the Blind." 2021 6th International Conference on Inventive Computation Technologies (ICICT). IEEE, 2021.

